\documentclass{tufte-book}

\newenvironment{loggentry}[2]% date, heading
{\noindent\textbf{#2}\marginnote{#1}\\}{\vspace{0.9cm}}

\begin{document} 
\begin{loggentry}{2015-Feb-19}{after snow afternoon}
	When there is nothing important to do, I am always going to watch video game match to make me relax. Ignorance and slack are now my biggest problems needed to be conquered.
\end{loggentry}

\begin{loggentry}{2015-Feb-19}{after snow evening}
	Humans are the creatures who are pretty good at using associative memeory method. In order to remember less and store more useful, we can create a knowledge net in our brain. Then we can get what we want quickly by going through key knowledge nodes. Life become easier if only we master well the basic skills on the path between nodes. When we accept new knowledge, a new node will be created and links will be made by the inner or outer relationship between them. Once the new knowledge are mastered well by us, the node will become messenger.
\end{loggentry}

\begin{loggentry}{2015-Feb-20}{after snow 12:55 Fri}
	All of us is have strong desire for victory. However, if we do not control it, life will become tense and nervous. Especially when we stuck at the deadly infinite loop, we may feel loss for a long time when failure comes. For this failure, there is big possibility since we are always in competing and comparing with others. What's worse, you are at the weakest time as you put yourself totally at thinking about whether you will be  a lose or winner and it can be the biggest disadvantege when others make use of you desire for winning. For me, I should not argue with others to prove me or him to be right or wrong. It is very stupid! 
\end{loggentry}
\begin{loggentry}{2015-Feb-20}{after snow 13::00 Fri}
	When a person can sit and spend some time to write a dinary, he becomes more mature and steady. It is also the time he start to recognize himself.
\end{loggentry}

\begin{loggentry}{2015-Feb-21}{after snow 13::00 Sat}
	What a pity it is that I can not drink since I like it very much but for study and research, I have to give up it.
\end{loggentry}

\end{document}